---
title: "DataProducts  Week4 - Reproducible Pitch"
author: "Rabeek Kanavapeer"
date: "5/14/2020"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(jpeg)
cap1 <- readJPEG("Week4_cap1.jpg",native=TRUE)
cap3 <- readJPEG("Week4_cap3.jpg",native=TRUE)
```

## Data Products - Week 4 - Reproducible Pitch

This slide is for the data science coursera course  data products for week 4 assignment. As part of this, I have created a shiny app and deployed it on the shiny server at and link is available at  https://rabeekraja.shinyapps.io/coviddatapresentation/. Code can be found at github at https://github.com/rabeekraja/dataproductsweek4.


## Overview

This project downloads previous date from current system date from European Centre for Disease Prevention and Control site and present COVID-19 cases worldwide.

This site having following things,
  1. Dynamic drop down for list of countries for a continent
  2. Tab of Summary
  3. Covid-19 summary for selected Continent & Country
  4. Covid-19 data sets for a selected Country
  5. Plotly interactive plot 
  6. +Ve cases for each day
  7. Deaths each day
  8. Cumulative Cases
  9. Cumulative Deaths

## Covid-19 Summary Screen shot 

```{r}
plot(0:1,0:1,type="n",ann=FALSE,axes=FALSE)
rasterImage(cap1,0,0,1,1)
```


## Covid-19 Plotly Screen shot 

```{r}
plot(0:1,0:1,type="n",ann=FALSE,axes=FALSE)
rasterImage(cap3,0,0,1,1)
```
